State and Parameter Estimation for a Spatio-Temporal Neural Fields

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
state parameter estimation update

The approximation of the state density is made by propagating the so called sigma points through the state-space model. The sigma points describe the mean and covariance of the state estimate. The number of sigma points needed is $2n_x+1$ where $n_x$ is the dimension of the stae space. The set of sigma points and their corresponding weights used in the UKF can be calculated as

>>>>

The approximation of the state density is made by propagating the so called sigma points through the state-space model. The sigma points describe the mean and covariance of the state estimate. The number of sigma points needed is $2\mathbf L+1$ where $\mathbf L$ is the dimension of the stae space. The  columns of the sigma point matrix and their corresponding weights used in the UKF can be calculated as
\begin{equation}
 \mathcal X_{0}=\bar x
\end{equation}
\begin{equation}
 \mathcal X_{i}=\bar x+(\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i \quad i=1, \dots, \mathbf L
\end{equation}
\begin{equation}
 \mathcal X_{i}=\bar x-(\sqrt{(\mathbf L + \lambda)\mathbf P_x})_{i-\mathbf L} \quad i=\mathbf L+1, \dots, 2\mathbf L
\end{equation}
\begin{equation}
 \mathbf W_0^{(m)}=\frac{\lambda}{\mathbf L+\lambda}
\end{equation}
\begin{equation}
 \mathbf W_0^{(c)}=\frac{\lambda}{\mathbf L+\lambda}+(1-\alpha^2+\beta)
\end{equation}
\begin{equation}
 \mathbf W_i^{(m)}=\mathbf W_i^{(c)}=\frac{1}{2(\mathbf L+\lambda)} \quad i=1, \dots, \mathbf 2L
\end{equation}
where the sacling parameter $\lambda$ is defined as
\begin{equation}
\lambda=\alpha^2(\mathbf L+\kappa)-\mathbf L 
\end{equation}
parameters $\alpha$, $\beta$ and $\kappa$ can be used to tune the filtering process \cite{Haykin2001}

% For explanation of $\lambda, \quad \alpha\quad\text{and}\quad\beta$ see \cite{wan2000unscented,Haykin2001}. $ (\sqrt{(\mathbf L + \lambda)\mathbf P_x})_i$ is the ith column of the matrix square root (e.g., lower-triangular Cholesky factorization). These sigma points propogated through the nonlinear function
